Appendix A: Comparision of lost/gained species to randomly selected species

### 2018-12-12 Appendix_A.Rmd
Korrekturen der Koauthoren übernommen.

# Function to prepare the res file for plotting
makesim <- function(EL, gain, sitem) {
  res <- tibble(aID_STAO = sites$aID_STAO, Sitemeasure = pull(sites[, paste(sitem)]))
  tmp <- map(res$aID_STAO, getsim, EL = EL, gain = gain)
  res$gain = gain
  res$EL = paste(EL)
  res$meanreal <- tmp %>% map_dbl("meanreal")
  res$mean <- tmp %>% map_dbl("mean")
  res$lower <- tmp %>% map_dbl("lower")
  res$upper <- tmp %>% map_dbl("upper")
  res
}
```
Temporal turnover is caused by species that are lost between surveys (or are overseen in the second survey) and/or are gained between surveys (or overseen during the first survey). It is likely that different drivers such as Nitrogen deposition or climate warming would cause different species to colonize or disappear from sites. Also methodological issues such as imperfect detection are likely to result in species with particular characteristics that are overseen in one survey and thus result in apparent species gains or losses. We here borrowed ideas from functional ecology in order to try to disentangle the potential drivers of species gains and losses: We compared the characteristics of the species that newly colonized or that disappeared from a site with the same amount of species that were randomly selected from all the species that were observed at the site (i.e. the species assemblage). Instead of the functional traits that are traditionally used in functional ecology such as species height, we used the Ellenberg values that we assumed could best reflect the main drivers that are likely to cause shifts in mountain hay plant communities. This were the Ellenberg values for temperature (that are likely to respond to climate warming), soil moisture (likely to respond to changes in precipitation), nutrients (likely to change in response to Nitrogen deposition and land-use intensity) and light (likely to change in response to land-use intensity).

>>>>

# Function to prepare the res file for plotting
makesim <- function(EL, gain, sitem) {
  res <- tibble(aID_STAO = sites$aID_STAO, Sitemeasure = pull(sites[, paste(sitem)]))
  tmp <- map(res$aID_STAO, getsim, EL = EL, gain = gain)
  res$gain = gain
  res$EL = paste(EL)
  res$meanreal <- tmp %>% map_dbl("meanreal")
  res$mean <- tmp %>% map_dbl("mean")
  res$lower <- tmp %>% map_dbl("lower")
  res$upper <- tmp %>% map_dbl("upper")
  res
}
```
Temporal turnover is caused by species that are lost between surveys (or are overseen in the second survey) and/or are gained between surveys (or overseen during the first survey). It is likely that different drivers such as Nitrogen deposition or climate warming would cause different species to colonize or disappear from sites. Also methodological issues such as imperfect detection are likely to result in species with particular characteristics that are overseen in one survey and thus result in apparent species gains or losses. We here borrowed ideas from functional ecology in order to try to disentangle the potential drivers of species gains and losses: We compared the characteristics of the species that newly colonized or that disappeared from a site with the same amount of species that were randomly selected from all the species that were observed at the site (i.e. the species assemblage). Instead of the functional traits that are traditionally used in functional ecology such as species height, we used the Ellenberg values that we assumed could best reflect the main drivers that are likely to cause shifts in mountain hay plant communities. These were the Ellenberg values for temperature (that are likely to respond to climate warming), soil moisture (likely to respond to changes in precipitation), nutrients (likely to change in response to Nitrogen deposition and land-use intensity) and light (likely to change in response to land-use intensity).
